### 2023-03-17 chapter0/chapter0.tex
Added some unorganized sentences to finish SLiMs paragraph and begin TF paragraph

Although the previous discussion has presented of disorder and structure as distinct phenomona , disorder is a spectrum
MorFs
folding on binding
fuzzy complexes

>>>>

SLiMs can also occur combinatorially.
Furthermore, SLiMs are easily tuned because PTMs or evolution can change their properties by modifying only a few residues. This dynamism and modularity is essential in signalling as it allows the efficient propagation and modulation of information.
Thus, they often function as hubs in networks of signaling pathways [CITATION]
Some IDRs are roughly like molecular computers which integrate signals from varying sources
As IDRs are highly flexible, they can bind to many partners, sometimes simultaneously, and therefore often act as hubs in these signaling networks.

Some of the most prominent examples of IDRs in cell signaling and regulation are the activation domains of transcription factors. Each cell expresses a unique complement of proteins that in large part determines its identity.

Although the previous discussion has presented of disorder and structure as distinct phenomona, disorder is a spectrum
MorFs
folding on binding
fuzzy complexes
